Fast Sorting on Modern Computers

### 2005-08-30 docs/tech_report/method.tex
fixed the merge method  more

%TODO this bit also has to be checked once we fix mergesort. if w fix mergesort
Once these sorts were written it was attempted to improve them slightly.
Instead of a tiled mergesort, a double-aligned tiled mergesort was written.
This aligned the arrays to avoid conflicts in the level 1 cache, at a slight
cost to level 2 cache performance. Double-aligned multi-mergesort was a
combination of this and of multi-mergesort. The rewrite was based on the base
mergesort, and was written far more cleanly, being more readable and efficient.
These were also found to reduce the instruction count, as well as the level 2
cache miss count. These results are discussed in more detail in Section
\ref{Mergesort results}.

>>>>

Once these sorts were written it was attempted to improve them slightly.
Instead of a tiled mergesort, a double-aligned tiled mergesort was written.
This aligned the arrays to avoid conflicts in the level 1 cache, at a slight
cost to level 2 cache performance. Double-aligned multi-mergesort was a
combination of this and of multi-mergesort. We also rewrote base mergesort far
more cleanly, with the results being more readable and efficient.  These were
also found to reduce the instruction count, as well as the level 2 cache miss
count. These results are discussed in more detail in Section \ref{Mergesort
results}.
